Towards a standardized evaluation of imputation routines

### 2022-03-31 index.Rmd
Add link to manuscript and checklist

- [The manuscript](LINK TO MANUSCRIPT)
- [The checklist](LINK TO CHECKLIST)

>>>>

- [The manuscript](https://github.com/gerkovink/evaluation/blob/main/Manuscript/Towards_a_standardized_evaluation_of_imputation_methodology.pdf)
- [The checklist](https://github.com/gerkovink/evaluation/blob/main/Checklist/Checklist.pdf)
